Project Setup

### 2024-09-12 setup.qmd
Implement Malika's feedback on the setup

If you haven't already, open RStudio. Then, click on _File_ > _New Project..._ to open the _New Project Wizard_.

@@

Also, we will utilize the package [`renv`](https://rstudio.github.io/renv/) to track the R packages our project depends on. Therefore make sure that the box _Use renv with this project_ is checked. Again, if this is the first time you are hearing about `renv`, have a look at the tutorial "[Introduction to {renv}](https://lmu-osc.github.io/introduction-to-renv/)".

@@

@@

A human-readable data dictionary is necessary for making one's research reproducible and the example we provided demonstrates only the bare minimum. A full data documentation including measurement instruments, sampling procedures, appropriate weighting, contact information, and more information about the study can be created with the R package [`pointblank`](https://rstudio.github.io/pointblank/articles/INFO-1.html). And one could go even further by making the information machine-readable in a standardized way. We provide an optional example of that in @nte-frictionless. If you want to learn more about the sharing of research data, have a look at the tutorial "[FAIR Data management](https://lmu-osc.github.io/FAIR-Data-Management/)".

@@

The manuscript also uses the Quarto extension "[apaquarto](https://wjschne.github.io/apaquarto/)", which needs to be installed in the project before it can be rendered:

@@

Also, you need to have a $\TeX$ distribution installed on your computer. A lightweight choice is [TinyTeX](https://yihui.org/tinytex/), which can be installed with Quarto as follows:

@@

- __Test your code.__ Test your code with scenarios where you know what the result should be. Turn bugs you discovered into test cases. Use linting tools, for example, the R package [`lintr`](https://lintr.r-lib.org/).

@@

`renv` only records the versions of R packages and of R itself. This means that potential system dependencies of R packages and other tools utilized in the project are not documented anywhere, including Quarto.^[As of August 2024, a proposal to record the version of Quarto and Pandoc has not been implemented, see [rstudio/renv#1143](https://github.com/rstudio/renv/issues/1143).] We will manually write them down when [creating a README](add_readme.qmd). For now, however, there is one simple step you can take to record the version of Quarto (and a few other dependencies). Do run the following:

>>>>

If you haven't already, open RStudio -- see @nte-terminal for an alternative to RStudio. Then, click on _File_ > _New Project..._ to open the _New Project Wizard_.

@@

Also, we will utilize the package [`renv`](https://rstudio.github.io/renv/) to track the R packages our project depends on. Using it makes it easier for others to view and obtain them at a later point in time. Therefore make sure that the box _Use renv with this project_ is checked. Again, if this is the first time you are hearing about `renv`, have a look at the tutorial "[Introduction to {renv}](https://lmu-osc.github.io/introduction-to-renv/)".

@@

::: {#nte-terminal .callout-note collapse="true"}
### Without RStudio

Without RStudio, one can create a Quarto project with version control and `renv` enabled by typing the following into a terminal:

```{.bash filename="Terminal"}
quarto create project default code-publishing-exercise
cd code-publishing-exercise/
rm code-publishing-exercise.qmd
git init
git checkout -b main
```

Then, one can open an R session, by simply typing `R` into the terminal. Next, sure that `getwd()` indicates that the working directory is `code-publishing-exercise`. If not, set it using `setwd("code-publishing-exercise")`. Then, initialize `renv`:

```{.r filename="Console"}
renv::init()
```
:::

@@

A human-readable data dictionary is necessary for making one's research reproducible and the example we provided demonstrates only the bare minimum. A full data documentation including measurement instruments, sampling procedures, appropriate weighting, contact information, and more information about the study can be created with the R package [`pointblank`](https://rstudio.github.io/pointblank/articles/INFO-1.html). And one could go even further by making the information machine-readable in a standardized way. We provide an optional example of that in @nte-frictionless. If you want to learn more about the sharing of research data, have a look at the tutorial "[FAIR Research Data management](https://lmu-osc.github.io/FAIR-Data-Management/)".

@@

The manuscript also uses the Quarto extension "[apaquarto](https://wjschne.github.io/apaquarto/)", which typesets documents according to the requirements of the @APA2020. It can be installed in the project using the following command:

@@

::: {#tip-apaquarto .callout-tip}
#### Not a psychologist?

If you are not a psychologist, you can also skip installing `apaquarto`. If you installed it by accident, run `quarto remove wjschne/apaquarto`.

Note, however, that the file `Manuscript.qmd` we prepared for you uses `apaquarto` by default and you need to set a different `format` in the YAML header if you decide not to use `apaquarto`:

```{.yml filename="Manuscript.qmd"}
format:
  pdf:
    pdf-engine: lualatex
    documentclass: scrartcl
    papersize: a4
```
:::

Also, you need to have a $\TeX$ distribution installed on your computer, which is used in the background to typeset PDF documents. A lightweight choice is [TinyTeX](https://yihui.org/tinytex/), which can be installed with Quarto as follows:

@@

- __Test your code.__ Test your code with scenarios where you know what the result should be. Turn bugs you discovered into test cases. Use linting tools^[A linting tool analyzes your code without actually running it. This process is called static code analysis.] to identify common mistakes in your code, for example, the R package [`lintr`](https://lintr.r-lib.org/).

@@

`renv` only records the versions of R packages and of R itself. This means that potential system dependencies of R packages and other tools utilized in the project are not documented anywhere, including Quarto.^[As of August 2024, a proposal to record the version of Quarto has not been implemented, see [rstudio/renv#1143](https://github.com/rstudio/renv/issues/1143).] We will manually write them down when [creating a README](make_readme.qmd). For now, however, there is one simple step you can take to record the version of Quarto (and a few other dependencies). Do run the following:
